Analysis2

### 2023-11-05 Lahman Analysis/Rough Analysis 2/Analysis2.qmd
Fix coding for park in small sample of players and add lower bound on sd in HR27c

```{r}
player_index_small <- Batting %>% 
  #Consider only two years to get a managable amount of players
  filter(yearID == 2018 | yearID == 2019) %>% 
  #Number the players for the multilevel model
  mutate(player_index = as.factor(playerID), .after = playerID) %>% 
  mutate(player_index = as.integer(player_index)) %>% 
  mutate(cAge = Age - 30, .after = Age) %>% 
  mutate(year_index = yearID - min(yearID) + 1, .after = yearID) %>%
  #For this test of conecpt we'll need to redefine the stadium's index since not all stadiums in the original dataset were used in 2018 and 2019
  select(!park_index) %>% 
  mutate(park_index = as.integer(park), .after = park)
```

>>>>

```{r}
player_index_small <- Batting %>% 
  #Consider only two years to get a managable amount of players
  filter(yearID == 2018 | yearID == 2019) %>% 
  #Number the players for the multilevel model
  mutate(player_index = as.factor(playerID), .after = playerID) %>% 
  mutate(player_index = as.integer(player_index)) %>% 
  mutate(cAge = Age - 30, .after = Age) %>% 
  mutate(year_index = yearID - min(yearID) + 1, .after = yearID) %>%
  #For this test of conecpt we'll need to redefine the stadium's index since not all stadiums in the original dataset were used in 2018 and 2019
  select(!park_index) %>% mutate(park = as.character(park)) %>%
  mutate(park = as.factor(park)) %>%
  mutate(park_index = as.integer(park), .after = park)
```
